Inferring generation-interval distributions from contact tracing data

### 2018-09-26 doc/network.tex
tweak

While the non-parametric method is simple, it does not use all available information from contact tracing data: it does not take into account who infected whom.
Assuming that infection occur as a poisson process in the beginning of an epidemic, we can obtain the following likelihood for the observed infection process:
\begin{equation}
\mathcal{L}(\RR, \theta) = \prod_{j=1}^N \left(\RR^{n_j} \exp \left(- \RR \int_0^{\tsub{t}{censor} - t_j} g(s;\theta) ds \right) \prod_{i=1}^{n_j} g(\tau_{i, j}; \theta) \right),
\end{equation}
where $N$ is the total number of infected individuals, $n_j$ is the number of individuals infected by $j$, $\tsub{t}{censor}$ is the time period which censoring was performed until, $t_j$ is the time at which infector $j$ was infected, $\tau_{i,j}$ is the observed generation interval between infector $j$ and infectee $i$, and $\theta$ is the (vector) parameter of the generation interval distribution $g$.
A similar method was proposed by \cite{forsberg2008likelihood} but it relies on discretized incidence reports and does not make assumptions about the shape of the generation-interval distribution.

\swp{I might say something about independence transmission events in the results if I decide to compare forsberg2008 as well -- see forsberg 2008...}

@@

\swp{May need to explain coverage...}
Surprisingly, both methods fail to reach nominal coverage.

>>>>

While the non-parametric method is simple, it does not use all available information from contact tracing data: it does not take into account who infected whom.
Assuming that infection occur as a poisson process in the beginning of an epidemic, we can obtain the following likelihood for the observed infection process:
\begin{equation}
\mathcal{L}(\RR, \theta) = \prod_{j=1}^N \left(\RR^{n_j} \exp \left(- \RR \int_0^{\tsub{t}{censor} - t_j} g(s;\theta) ds \right) \prod_{i=1}^{n_j} g(\tau_{i, j}; \theta) \right),
\end{equation}
where $N$ is the total number of infected individuals, $n_j$ is the number of individuals infected by $j$, $\tsub{t}{censor}$ is the time period which censoring was performed until, $t_j$ is the time at which infector $j$ was infected, $\tau_{i,j}$ is the observed generation interval between infector $j$ and infectee $i$, and $\theta$ is the (vector) parameter of the generation interval distribution $g$.
A similar method was proposed by \cite{forsberg2008likelihood} but it relies on discretized incidence reports rather than the observed generation intervals.

\swp{I might say something about independence transmission events in the results if I decide to compare forsberg2008 as well -- see forsberg 2008...}
\swp{I got stuck on forsberg 2008. I get weird estimates with wide confidence intervals but I feel like that's what their method is supposed to do (based on figure 3 in their paper). It doesn't use generation interval either so I think we can just ignore it?}

@@

\swp{May need to explain what coverage is...}
Surprisingly, both methods fail to reach nominal coverage.
